---
title: "MATHS 1006 Data Taming Assignment Five Questions"
author: "Huining H"
date: "20/10/2021"
output:
  html_document:
    df_print: paged
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
pacman::p_load(knitr,dplyr)
pacman::p_load(tidyverse, inspectdf,tidyr,stringr, stringi)
pacman::p_load(caret,modelr)
pacman::p_load(mlbench,mplot)
pacman::p_load(tidymodels,glmx)
pacman::p_load(skimr,vip,yardstick,ranger,kknn)
pacman::p_load(themis)
```

# Data Cleaning

Q1.
```{r data_affairs}
affairs <- read.csv(file = 'affairs.csv')%>%
   as_tibble()
head(affairs,6)
```

Q2.

Affair is the outcome variable, sex, age, ym, child, religious, education, occupation and rate are the predictor variables.


Q3.

```{r skim_affairs}
affairs %>% 
  skim()
```

There is no missing data. 601 observations and 9 variables. 4 variables been read in incorrectly.


Q4.

```{r bi_r_affairs_convert}
affairs$affair <- ifelse(affairs$"affair"==1,"yes","no")
affairs_c <- 
  affairs %>% 
  mutate_at(c("religious","education","occupation","rate"), as.character)

affairs_c <- 
  affairs_c %>% mutate_if(is.character, as.factor)
```


Q5.

```{r skim_affairs_c}
affairs_c %>% 
  skim()
```


a.
150 people responded as having had an affair. 430 people responded to having children.


b.
```{r age_rel_affairs}
mean(affairs$age)
mean(affairs$religious)
```
The mean age of respondents is 32.48752. 
The mean response on the religious scale is 3.116473.

# Exploratory analysis

1.

```{r f_affairs}
affairs_c %>% 
  group_by(affair, sex) %>% 
  summarize(n=n()) %>%
  mutate(rel.freq = paste0(round(100 * n/sum(n), 0), "%"))
```
Of the participants who responded “no” to an affair, 54% of them are female. For those who responded “yes” to having an affair is 48%. There appear to be a difference in the proportion of females who will have an affair opposed to those who will not.

2.

```{r child_affairs}
affairs_c %>% 
  group_by(affair, child) %>% 
  summarize(n=n()) %>%
  mutate(rel.freq = paste0(round(100 * n/sum(n), 0), "%"))
```

82% participants who responded “yes” to having an affair had children. 68% participants who responded “no” had children, 32% participants who responded “no” had no children, Based on this, you are more likely to have children if you have an affair. 

# Split and preprocess

1. 

```{r split_affairs}
set.seed(123)
affair_split <- initial_split(affairs_c)
affair_split
```

450 observations are in the training set and 151 are in the testing set。


2.

```{r test_train_affairs}
affair_train <- training(affair_split )
affair_test <- testing(affair_split)
head(affair_train,6)
```

3.

see ?step_downsample

"This function creates a specification of a recipe step that will remove rows of a data set to make the occurrence of levels in a specific factor level equal."

It reduces the dimensional of the data to a more manageable size and enabling in faster processing of the data.


4.

```{r recipe_affairs}
affair_recipe <- recipe( affair ~ ., data = affair_train) %>%
  step_downsample(affair)%>%
  step_dummy(sex,child,religious,education,occupation,rate)%>%
  step_normalize(all_predictors() )
affair_recipe
```

```{r prep_affairs}
affair_prepped <- affair_recipe %>% 
  prep()
affair_prepped
```

5.

```{r juice_affairs}
affair_prepped_j <- juice(affair_prepped)
```


```{r bake_affairs}
affair_recipe_t <- recipe( affair ~ ., data = affair_test) %>%
  step_downsample(affair)%>%
  step_dummy(sex,child,religious,education,occupation,rate)%>%
  step_normalize(all_predictors() )

affair_prepped_t <- affair_recipe %>% prep()
affair_prepped_t
affair_prepped_b <- bake(affair_prepped_t, new_data = NULL)
```


6.
```{r skim_training_affairs}
affair_prepped_j %>% 
  skim()
```

No, losing data on sex_female and child_no and so on in step_downsample. Normalization and prep() have done what expected.

# Tune and fit a model

1.

```{r nearest_neighbours_affairs}
aff_neighbour_spec <- nearest_neighbor( mode = "classification", neighbors = tune() )%>% 
 set_engine( "kknn" )
aff_neighbour_spec 
```

2.

```{r validation_set_affairs}
set.seed(1223)
affairs_cv <- vfold_cv( affair_prepped_j, v = 5 )
```


3.
```{r grid_affairs}
a_grid <- grid_regular(neighbors(),levels = 25)
```

4.

```{r tune_affairs}

a_wf <- workflow() %>%
  add_model(aff_neighbour_spec) %>% 
  add_formula(formula = affair ~ .)

a_tuned <- tune_grid(a_wf,
                     resamples = affairs_cv,
                     grid = a_grid)
```

5.

```{r best_affairs}
best <- select_best(a_tuned)
best
```

6.

```{r Finalise_affairs}
finalize_model(aff_neighbour_spec, best)
```

7.

```{r fit_affairs}
affairs_knn <- aff_neighbour_spec %>% 
 fit( affair ~ ., data = affair_prepped_j )
affairs_knn
```

# Evaluation 

1.
```{r predict_affairs}
test_pred <- predict( affairs_knn, affair_prepped_b, type = "class" )
head(test_pred,6)
```


2. 
```{r bind_affairs}
bind_grid <- test_pred %>% 
 bind_cols(test_pred, affair_prepped_b) %>%  rename(
  affair_p1 = .pred_class...1, affair_p2 = .pred_class...2,
 )

```



3.
```{r cunfusion_affairs}
library(cvms)
conf_mat <- confusion_matrix(targets = bind_grid$affair,
                             predictions = bind_grid$affair_p1)

plot_confusion_matrix(conf_mat$`Confusion Matrix`[[1]])
```
4.
sensitivity 57/(57+54) = 0.5135135, predict having affairs that are actually having affairs is 0.5135135.
specificity 89/(89+22) = 0.8018018, predict not having affairs that are actually not having affairs is 0.8018018.


5.
```{r tibble_affairs}
tb <- tibble(
  'sex' = "male", 
  'age' = "47",
  'ym' = "15",
  'occupation' = "6",
  'child' = "no",
  'religious' = "2",
  'education' = "20",
  'rate' = "5",
)
tb
```







