---
title: "Assignment Two"
author: "Huining H"
date: "20/08/2021"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
pacman::p_load(knitr,dplyr)
pacman::p_load(tidyverse, inspectdf,tidyr,stringr, stringi)
```


# Question One: Reading and Cleaning

```{r read_ashes, echo=TRUE}
ashes <- read.csv(file = 'ashes.csv')
```


**a. Tidy Data**

```{r ashes_long}
ashes_long <- ashes %>% 
  pivot_longer(
    cols = 4:13, 
    names_to = "Innings", 
    values_to = "Performance", 
    values_drop_na = TRUE
  )
ashes_long
```


```{r ashes_P, include=FALSE}
ashes_longP <- c(ashes_long[, 5])
ashes_longP
```

#typeof(ashes_longP)
#unlist(ashes_longP)
#is.vector(ashes_longP)
#is.vector(details)
#typeof(details)
#stringi:::stri_prepare_arg_string(ashes_longP)
#library(stringr)
#as.vector(details)

```{r ashes_long2}
unl_P <- unlist(ashes_longP)
details <- str_match(unl_P, "number (\\d+), scored (\\d+) runs from (\\d+)")

df  <- tibble(
  text = unl_P, 
  number = details[, 2],
  scored = details[, 3],
  balls = details[, 4]
  )
df
```

```{r ashes_bind}
part_1 <- ashes_long[ ,1:4]
part_2 <- df[ ,2:4]
ashes_bind <- bind_cols(part_1, part_2)
ashes_bind
```


**b. Recode**


```{r ashes_lv}
ashes_lv <- sapply(ashes_bind, n_distinct)
ashes_lv
```



```{r ashes_recode}
ashes_bind$team <- as.factor(ashes_bind$team)
ashes_bind$role <- as.factor(ashes_bind$role)
ashes_bind$number <- as.integer(ashes_bind$number)
ashes_bind$scored <- as.integer(ashes_bind$scored)
ashes_bind$balls <- as.integer(ashes_bind$balls)
ashes_bind
```

**c. Clean**

levels(ashes_bind$team)
levels(ashes_bind$role)

```{r clean1}
levels(ashes_bind$team)[3] <- "England"
levels(ashes_bind$role)[2] <- "all-rounder"
```

```{r clean2}
levels(ashes_bind$role)[2] <- "all-rounder"
```

```{r clean3}
levels(ashes_bind$role)[2] <- "batsman"
```

```{r clean4}
levels(ashes_bind$role)[3] <- "batsman"
```

```{r clean5}
levels(ashes_bind$role)[3] <- "bowler"
```

```{r check}
ashes_bind
```




# Question Two: Univariate Analysis

**a. Score histogram**

```{r ashes_his}
p1 <- ggplot(ashes_bind, aes(x=scored, color=team, fill=team)) +
      geom_histogram(position="dodge", alpha=0.5)+
      scale_color_manual(values=c("#999999", "#E69F00"))+
      scale_fill_manual(values=c("blue", "black"))+
      labs(title="Histogram of scores",x="Score")+
      theme_classic()
p1
```
**b. Describe the distribution of scores**

* shape 
  - Skewed right.
* location 
  - median = 18
```{r median}
median(ashes_bind$scored, na.rm = TRUE)
```

* spread 
  - range = 0-244, variance = 1706, standard deviation = 41
```{r spread}
range(ashes_bind$scored, na.rm = TRUE)
var(ashes_bind$scored,na.rm = TRUE)
sd(ashes_bind$scored,na.rm = TRUE)
```
* outliers 
    ->244


```{r outliers}
library(outliers)
test <- grubbs.test(ashes_bind$scored)
test
```


**c. Bar chart**

```{r bar}
p2 <- ggplot(ashes_bind, aes(x=team, color=role, fill=role)) +
      geom_bar(position="dodge", alpha=0.5)+
      scale_color_manual(values=c("#999999", "#E69F00","#FF0000", "#0000FF"))+
      scale_fill_manual(values=c("blue", "black","darkgreen","grey"))+
      labs(title="Bar chart of teams participating in the series",x="Team")+
      theme_classic()
p2
```
```{r player}
t1 <- table(ashes_bind$team)/10
t1
```

13 players were used by Australia  team in the series;\
14 players were used by England   team in the series.

# Question Three: Scores for each team

**a. Histograms faceted by team**

```{r ashes_his_2}
p3 <- ggplot(ashes_bind, aes(x=scored, color=team, fill=team)) +
      geom_histogram(position="dodge", alpha=0.5)+
      scale_color_manual(values=c("#999999", "#E69F00"))+
      scale_fill_manual(values=c("blue", "black"))+
      labs(title="Histogram of scores",x="Score")+
      facet_grid(team ~ .) +
      theme_classic()
p3
```


**b. Side-by-side boxplots**

```{r ashes_box}
p4 <- ggplot(ashes_bind, aes(x=scored, y = team, color=team, fill=team)) +
      geom_boxplot()+
      scale_color_manual(values=c("#999999", "#E69F00"))+
      scale_fill_manual(values=c("navy", "black"))+
      labs(title="Side-by-side boxplots of scores",x="Score", y ="Team")+
      coord_flip()+
      theme_classic()
p4
```


**c. Average score**

```{r ashes_his_3}
library(plyr)
me <- ddply(ashes_bind, "team", summarise,
            grp.mean=mean(scored,na.rm = TRUE))
p3_1 <- ggplot(ashes_bind, aes(x=scored, color=team, fill=team)) +
        geom_histogram(position="dodge", alpha=0.5)+
        labs(title="Histogram of scores",x="Score")+
        facet_grid(team ~ .) +
        geom_vline(data=me, aes(xintercept=grp.mean),
             linetype="dashed")+
        scale_color_manual(values=c("#999999", "#E69F00"))+
        scale_fill_manual(values=c("blue", "black"))+
        theme_classic()
p3_1
```

* From the Histogram of scores above, team Australia have had a higher average score.

* Side-by-side boxplots of scores above, team Australia have had a higher average score.

The distributions of scores
  -> see Question Two b.

# Question Four: Scoring rates

**a. scatterplot **

```{r scatter}
p5 <- ggplot(ashes_bind, aes(x=number, y = scored, color=team, shape=team)) +
      geom_point() +
      scale_color_manual(values=c("#999999", "#E69F00"))+
      scale_fill_manual(values=c("navy", "black"))+
      labs(title="Scatterplot of scores against number of balls",
           x="Balls", y ="Scored")+
      geom_smooth(se=FALSE, fullrange=TRUE)
      theme_classic()
p5
```

**b. relationship**

no relationship. Players who face more balls NOT likely to score more runs.


**c. scoring_rate**

```{r scoring_rate}
scoring_rate <-
  ashes_bind$number/ashes_bind$balls
p6 <- ggplot(ashes_bind, aes(x=number, y = scoring_rate, color=team, shape=team)) +
      geom_point() +
      scale_color_manual(values=c("#999999", "#E69F00"))+
      scale_fill_manual(values=c("navy", "black"))+
      labs(title="Scatterplot of scoring rate against number of balls",
           x="Balls", y ="scoring rate")+
      geom_smooth(se=FALSE, fullrange=TRUE)
      theme_classic()
p6
```


**d. relationship between scoring rate and number of balls**

- Yes,there is a relationship between scoring rate and number of balls;\
  players who face more balls may likely to score runs more quickly.

# Question Five: Teams’ roles

**a. bar chart of the number of players on each team participating in the series**

```{r p2}
p2
```


**b. contingency table**



{r contingency table}
tablec <- ashes_bind%>%
            group_by(role, team)%>%
            summarize(n=n())%>%
            mutate(prop=n/sum(n))%>%
            subset(select=c("role","team","prop"))%>%
            spread(role, prop)%>%
            kable()
tablec
```

c

Aus team is made up of a larger proportion of batters\
England contains a larger proportion of all-rounders

