---
title: "Assignment Four"
author: "Huining H"
date: "17/09/2021"
output: pdf_document
---

# Summary

# Method

## Bivariate summaries

Bivariate summaries is used to find the relationship between evaporation and potential 5 influences: Month, Day of the week,maximum temperature in degrees Celsius, Minimum temperature in degrees Celsius, and Relative humidity, as measured at 9am.

See appendix Bivariate summaries.

Quantitative variables:
Figure 1 indicating a medium positive correlation between Minimum temperature in degrees Celsius and Evaporation.  
Figure 2 indicating a weak positive correlation between Maximum temperature in degrees Celsius and Evaporation.  
Figure 3 indicating a negative correlation between Relative humidity, as measured at 9am and Evaporation.  


Categorical variables:
Figure 5 indicating the trend of month and Evaporation:high at Jan then decrease in the first six months of the year and reach the low point at Jun and increase gradually in the rest of the months. 

Figure 6 indicating no obvious relation between Day of the week and Evaporation

## Model selection

Quantitative variables:
From the summary table of all quantitative variables, Maxmum temperature in degrees Celsius has a p-value higher than 0.05 (> 0.05) thus is not statistically significant. From table 4,Minimum temperature and Relative humidity both have p-value  less than 0.05 (<2e-16), they are statistically significant.

Categorical variables:
From table 3, Day of the week has small F value and  p-value higher than 0.05 (> 0.05), therefore not statistically significant. In Table 5 , Month has a p-value  2.2e-16 ***, less than 0.05, it is statistically significant. 

These significant terms seems not differ from what concluded from the bivariate analyses above except for Maximum temperature in degrees Celsius and Evaporation.
It may due to that bivariate analyses study the correlation measures the degree of a relationship between two variables, where regression is how explanatory  variables affect Response variables, in here is amount of evaporation in a day.

From table 6, the p-value is less than 0.05 in the interaction term between month and 9am relative humidity is statistically significant, humidity seems has a different effect in different months.




# Results

## Model interpretation

Quantitative variables:

The Coefficients Estimate of the model is 7.098, it is one unit increase in Minimum temperature/Relative humidity then expected change in evaporation in a day in mm. In here, one degrees Celsius Minimum temperature change then 0.436mm change in evaporation; one unit Relative humidity at 9am change then -0.102 mm change in in evaporation.


Categorical variables:
Month has P value reduced greatly compare to the lm()output and the p_value is < 0.05. The large F value indicate the variance between months significantly larger than within month.



# Conclusions





# Prediction

For January 13,2020 can we say with 95% confidence that this will occur.

For all other date can we say with 95% confidence that this will not occur.

see appendix Prediction selection.



# Appendix

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
pacman::p_load(knitr,dplyr)
pacman::p_load(tidyverse, inspectdf,tidyr,stringr, stringi)
pacman::p_load(caret,modelr)
pacman::p_load(mlbench,mplot)
pacman::p_load(tidymodels)
```

## Bivariate summaries

```{r data_melbourne}
melbourne <- read.csv(file = 'melbourne.csv')
```


```{r data_melbourne_date}
melbourne_date <- melbourne %>% mutate_at(vars(Date), as.Date, format="%Y-%m-%d")
# head(melbourne_date)
```


```{r data_melbourne_date1}
library(lubridate)
mel_month <- month(as.POSIXlt(melbourne_date$Date, format="%d/%m/%Y"))
mel_week <- weekdays(as.POSIXlt(melbourne_date$Date, format="%d/%m/%Y"))
```

Table 1. a table including all variables used in the analysis.
```{r data_melbourne_date2}
melbourne_6 <- melbourne_date %>%
   as_tibble() %>%
   select( c(2,3,5,11) ) %>%
   bind_cols(mel_month,mel_week)
head(melbourne_6)
```

change column name.
```{r data_melbourne_colname}
colnames(melbourne_6) <- c("Min_temp", "Max_temp","Evaporation",
                           "am_humidity","Month","Day")
#head(melbourne_6)
```

 ```{r data_melbourne_conver}
melbourne_6 <- melbourne_6 %>% mutate(Month = as.character(Month))

head(melbourne_6)
```
change month to monthabb
```{r data_melbourne_mconver}
m_months <- c("Jan","Feb","Mar",
              "Apr","May","Jun",
              "Jul","Aug","Sep",
              "Oct","Nov","Dec")
melbourne_6$MonthAbb <- m_months[melbourne_6$Month]
head(melbourne_6)
```




Figure 1. a scatter plot of Evaporation on y-axis, Minimum temperature in degrees Celsius on the x-axis.
```{r melbourne_relat_mint}
ggplot(melbourne_6, aes(x = Min_temp, y = Evaporation)) + 
  geom_point()  + 
  labs(y = "Evaporation", x = "Min_temp") + 
  scale_color_brewer(palette = "Set1")
```



Figure 2. a scatter plot of Evaporation on y-axis, Maximum temperature in degrees Celsius on the x-axis.
```{r melbourne_relat_maxt}
ggplot(melbourne_6, aes(x = Max_temp, y = Evaporation)) + 
  geom_point()  + 
  labs(y = "Evaporation", x = "Max_temp") + 
  scale_color_brewer(palette = "Set1")
```

Figure 3. a scatter plot of Evaporation on y-axis, Relative humidity, as measured at 9am on the x-axis.
```{r melbourne_relat_humid}
ggplot(melbourne_6, aes(x = am_humidity, y = Evaporation)) + 
  geom_point()  + 
  labs(y = "Evaporation", x = "9am_humidity") + 
  scale_color_brewer(palette = "Set1")
```
Figure 4. a boxplot of Evaporation on y-axis, Month on the x-axis.
```{r melbourne_relat_Month}
ggplot(melbourne_6, aes(x = reorder(MonthAbb,Month), 
                        y = Evaporation)) + 
  geom_boxplot()  + 
  labs(y = "Evaporation", x = "Month") + 
  scale_color_brewer(palette = "Set1")
```

Figure 5. a boxplot of Evaporation on y-axis, Day of the week on the x-axis.
```{r melbourne_relat_day}
ggplot(melbourne_6, aes(x = Day, y = Evaporation)) + 
  geom_boxplot()  + 
  labs(y = "Evaporation", x = "Day") + 
  scale_color_brewer(palette = "Set1")
```

## Model selection

fit a model
```{r melbourne_createmodel}
melbourne.c  <- workflow() %>%
  add_formula(Evaporation ~ Min_temp+ Max_temp+
                     am_humidity+ Month + Day) %>%
  add_model(linear_reg() %>%
  set_engine("lm")) %>%
  fit(melbourne_6)
#melbourne.c
```

Table 1. a summary table of all variables.
```{r melbourne_lm}
melbourne.all  <- lm( Evaporation ~ Min_temp+ Max_temp+
                     am_humidity+ Month + Day, data = melbourne_6)
summary(melbourne.all)
```


Table 2. a summary table of quantitative variables.
```{r melbourne_quantitative_lm}
melbourne.lm  <- lm( Evaporation ~ Min_temp+ Max_temp+
                     am_humidity, data = melbourne_6)
summary(melbourne.lm)
```


Table 3. an anova table of categorical variables.
```{r melbourne_cate_anova}
melbourne.lmc  <- lm( Evaporation ~ Month + Day, data = melbourne_6)
anova(melbourne.lmc)
```

Table 4. a summary table of quantitative variables with max temperture removed.
```{r melbourne_model_3}
melbourne.lm3  <- lm( Evaporation ~  Min_temp+ am_humidity, data = melbourne_6)
summary(melbourne.lm3)
```

Table 5. an anova table of categorical variables with Day of the week removed.

melbourne.lm4  <- lm(Evaporation ~  MonthAbb, data = melbourne_6)
anova(melbourne.lm4)



Table 6. an anova table of interaction term between month and 9am relative humidity.

melbourne.lmi  <- lm( Evaporation ~ MonthAbb+ am_humidity + 
                      MonthAbb:am_humidity, data = melbourne_6)
anova(melbourne.lmi)



## Model interpretation




## Model diagnostics

```{r melbourne_modelgvl}
library(gvlma)
gvmodel <- gvlma(melbourne.lm3)
summary(gvmodel)
```

```{r melbourne_residuals1}
melbourne_mint  <- lm( Evaporation ~  Min_temp, data = melbourne_6)
plot(fitted(melbourne_mint), resid(melbourne_mint), col = "grey", pch = 20,
     xlab = "Fitted", ylab = "Residuals", main = "Fitted versus residuals plot")
abline(h = 0, col = "darkorange", lwd = 2)
plot(melbourne_mint, which = 1)
plot(melbourne_mint, which = 3)
```

```{r melbourne_residuals2}
melbourne_hum  <- lm( Evaporation ~  am_humidity, data = melbourne_6)
plot(fitted(melbourne_hum), resid(melbourne_hum), col = "grey", pch = 20,
     xlab = "Fitted", ylab = "Residuals", main = "Fitted versus residuals plot")
abline(h = 0, col = "darkorange", lwd = 2)
plot(melbourne_hum, which = 1)
plot(melbourne_hum, which = 3)
```

```{r melbourne_QQ1}
qqnorm(resid(melbourne_mint), main = "Normal Q-Q Plot", col = "darkgrey")
qqline(resid(melbourne_mint), col = "dodgerblue", lwd = 2)
plot(melbourne_mint, which = 2)
```

```{r melbourne_QQ2}
qqnorm(resid(melbourne_hum), main = "Normal Q-Q Plot", col = "darkgrey")
qqline(resid(melbourne_hum), col = "dodgerblue", lwd = 2)
plot(melbourne_hum, which = 2)
```

# Prediction

```{r melbourne_lmp}
melbourne.lmp  <- lm( Evaporation ~  Min_temp+ am_humidity, data = melbourne_6)
```



```{r melbourne_predic1}
new_data1 <- tibble(Min_temp = 13.8,am_humidity = 74)
predict1 <- predict(melbourne.lmp, new_data1, interval = "confidence")
predict1 <- as_tibble(predict1)
```

```{r melbourne_predic2}
new_data2 <- tibble(Min_temp = 16.4,am_humidity = 57)
predict2 <- predict(melbourne.lmp, new_data2, interval = "confidence")
predict2 <- as_tibble(predict2)
```

```{r melbourne_predic3}
new_data3 <- tibble(Min_temp = 26.5,am_humidity = 35)
predict3 <- predict(melbourne.lmp, new_data3, interval = "confidence")
predict3 <- as_tibble(predict3)
```

```{r melbourne_predic4}
new_data4 <- tibble(Min_temp = 6.8,am_humidity = 76)
predict4 <- predict(melbourne.lmp, new_data4, interval = "confidence")
predict4 <- as_tibble(predict4)
```

```{r melbourne_predic}
melbourne_pred <- 
  bind_rows(predict1,predict2,predict3,predict4)
rownames(melbourne_pred) <- c("1","2","3","4")
melbourne_pred
```


