---
title: 'Quantitative Variables: Location, Spread and Histograms'
author: "E"
date: "18/08/2021"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
pacman::p_load(knitr)
pacman::p_load(tidyverse, inspectdf)
```

## quantitative variables - describe the centre and spread of the data
## For continuous variables - the mean and standard deviation.

## Picking the column displ - which records the mean engine displacement in litres

```{r mean_sd}
mean(mpg$displ)
sd(mpg$displ)
```


Statisticians often talk about the 'five-number summary', describes a distribution of data in five numbers.

1. sample minimum or smallest value
1. first (or lower) quartile.
1. median (or middle) value.
1. third (or upper) quartile.
1. sample maximum or largest value.


```{r summary_d}
summary(mpg$displ)
```

# summary(mpg$displ)

## visualise the entire distribution by creating a histogram using ggplot

```{r his_d}
ggplot(mpg,aes(x = displ)) + geom_histogram(col = "black")
```

ggplot(mpg,aes(x = displ)) + geom_histogram(col = "black")



