---
title: "Tutorial2"
author: "E"
date: "15/08/2021"
output:
  pdf_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
pacman::p_load(knitr)
```

1. Create a file - some sort of reproducible report - that can incorporate your explanations, code and output (analysis and plots etc).

### Solution
Create a R Markdown file

2. Load the diamonds dataset. This is saved in the tidyverse package.
# Solution

```{r data1}
pacman::p_load(tidyverse, inspectdf)
diamonds
```


3. Check the data to see if there are any entries missing (i.e. are there any NA’s?).

```{r data2}
diamonds %>% inspect_na()
```



4. Determine how many types of cut there are. What are they? Show how many diamonds there are of each particular cut.

```{r data3}
unique(diamonds$cut)
```

```{r data4}
count(diamonds, cut)
```

5. Your boss wants to know whether the price of the diamonds depends more on cut or color Using ggplot, produce two side-by-side boxplots of price, one using cut and one using color. Which variable appears to affect price more, cut or color?

```{r data5}
ggplot(diamonds, aes(x=cut, y = price, fill = cut)) +
geom_boxplot()
```

```{r data6}
ggplot(diamonds, aes(x=color, y = price, fill = color)) +
geom_boxplot()
```
## Colour appears to affect price more



6. If a customer wants to buy a Premium diamond, with color rating J, how much should they expect to pay on average
```{r data7}
diamonds %>%
filter(cut == "Premium", color == "J") %>%
summary()
```
6. If a customer wants to buy a Premium diamond, with color rating J, how much should they expect to pay on average?







```{r cars}
summary(cars)
```

## Including Plots

You can also embed plots, for example:

```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
